\LARGE \bf Human-Robot Interaction: Tackling the AI Challenges

### 2013-09-05 paper.tex
Tweaking and more tweaking

\documentclass[preprint,5p]{elsarticle}

@@

\usepackage[draft, nomargin, marginclue, footnote]{fixme}

@@

\listoffixmes

@@

\subsection{The human-robot interaction challenge}\label{sec:problem}

@@

\fxfatal{Merge the following 3 paragraphs}
Our frame is the robot which is
expected to achieve interactive object manipulation, fetch and carry tasks and
similar tasks in a domestic environment (Figure~\ref{fig:hri-dec}).

We envision HRI in a context where two agents (a human and a robot)
share a common space and exchange information through various
modalities. Our aim is to endow the robot with an explicit
consideration of the human and with the ability to manage its
interactions with him (Figure~\ref{fig:hri-dec}). This must be
considered at the architecture level as well as at the task/motion
planning and execution level.

Over the last years we have focused our efforts on identifying the cognitive
prerequisites of these challenges, and giving them experimental reality on the
robots: what is required for sentences like ``Let's set the table together''
to be understood by the robot, correctly interpreted in the spatial and
temporal context of the interaction, and eventually transformed into a set of
actions.

The problem we are dealing with here
is the following. Given:

\begin {itemize}
\item a joint goal, which has been previously established and agreed
  upon (through a process which is out of the scope of this paper),
\item the current situation, acquired through perception or
  deduction from previous perceptions, including the state of the
  environment of the robot and of the human,
\item {\it a priori} common-sense knowledge,
\end {itemize}

@@

\begin {itemize}
\item to build and maintain relevant robot and human beliefs
  (from the robot perspective) with respect to state of the world and the task,
\item to build and maintain iteratively shared (human-robot) plans, 
\item to refine and execute the actions it has to perform, and to monitor 
those achieved by its human partner.
\end {itemize}

@@

\subsection{Our contributions towards the cognitive robot}

The main scientific contributions of the article are summarized here, to guide
the reader. We develop and discuss them, also in relation to other works, at
the end of the article.

\fxfatal{Rewrite section 'summary of contributions'}

@@

The next section presents the overall architecture and the knowledge model we
have developed for our robots. Section~\ref{sec:impl} gives some insights on
the each of the main components of the architecture, and try to highlight their
significance for artificial intelligence. Section~\ref{sec:expe} presents two
experiments that illustrate in a concrete way what can be currently achieved
with our robots.  Section~\ref{sect|conclusion} finally summarizes our main
contribution and relate them to other recent researches in the field.

@@

\fxfatal{Need to carefully introduce this section: how did we come up this this architecture?}

\fxfatal{Describe archi}

@@

\fxwarning{Relate HATP social rules to other AI techniques}

@@

\fxfatal{Insert here discussion of other major KRR systems for robots (Severin)}

@@

\fxfatal{Introduce the paragraph}

@@

The human presence brings new requirements for robot's abilities both
at the functional and at the deliberative levels~\cite{Klein2004}. The
topics involve motion~\cite{Kulic2007,Berg2004,Madhava2006},
navigation~\cite{Althaus2004,Sisbot2007}, manipulation~\cite{Kemp2007}
in presence of humans as well as perception of human
activities~\cite{Breazeal2001,Burger2008}. Also, when
interacting with humans, robots need to incorporate communication and
collaboration abilities. Several theories dealing with
collaboration~\cite{Cohen1991,Grosz1996,Clark1996} emphasize that
collaborative tasks have specific requirements compared to individual
ones, \eg, since the robot and the person share a common goal, they
have to agree on the manner to realize it, they must show their
commitment to the goal during execution, etc. Several robotic systems
have already been built based on these
theories~\cite{Rich1997,Sidner2005,Breazeal2003} and they
all have shown benefits of this approach\fxwarning{which approach? how it is related to larger AI challenges?}. They have also shown how
difficult it is to manage turn-taking between communication partners
and to interleave task realization and communication in a generic
way\fxwarning{is it smthg we improve one?}. Finally, today only few
systems~\cite{Fong2006,Breazeal2003,Sisbot2008} take humans into
account at all levels\fxwarning{Old references, no new ones? we should also say what is new/better with our approach (Rachid)}.

@@

\fxfatal{Rewrite conclusion}

>>>>

%\documentclass[preprint,5p]{elsarticle}
\documentclass[final,3p,times]{elsarticle}

@@

\usepackage[draft,nomargin, marginclue, footnote]{fixme}

@@

@@

We scope our work to the robot which is
expected to achieve interactive object manipulation, fetch and carry tasks and
similar tasks in a domestic environment (Figure~\ref{fig:hri-dec}).

Two agents (a human and a robot) share a common space and exchange information
through multiple modalities. The robot is expected to explicitly take into
account the human and to manage its interactions with him.

Namely, the robot must be able to recognize, understand and participate
to communication situations, both explicit (\eg the human addresses verbally
the robot) and implicit (\eg the human points to an object); the robot must be
able to take part to joint actions, both proactively (by planning and proposing
such an action to the human) and reactively; the robot must be able to move and
act in a safe, efficient and legible way, taking into account social rules like
proxemics.

@@

Those three items have broad implications regarding the required underlying
cognitive skills.  A \emph{joint action}, for instance, can be described as
follow. Given:

\begin {itemize}
\item a joint goal, which has been previously established and agreed
  upon (typically through dialogue),
\item the current situation, acquired through perception or
  deduction from previous perceptions, including the state of the
  environment of the robot and of the human,
\item {\it a priori} common-sense knowledge,
\end {itemize}

@@

\begin{itemize}
\item to build and maintain relevant robot and human beliefs
  (from the robot perspective) with respect to state of the world and the task,
\item to build and maintain iteratively shared (human-robot) plans, 
\item to refine and execute the actions it has to perform, and to monitor 
those achieved by its human partner.
\end{itemize}

@@

We will see, in the following sections, how cognitive skills for realistic
human-robot interaction can be implemented and organized together in a coherent
architecture.

@@

The next section presents the overall architecture and the knowledge model we
have developed for our robots. Section~\ref{sec:impl} gives some insights on
the each of the main components of the architecture, and try to highlight their
significance for artificial intelligence. Section~\ref{sec:expe} presents two
experiments that illustrate in a concrete way what can be currently achieved
with our robots.  Section~\ref{sect|conclusion} finally summarizes our main
contributions and relate them to other recent researches in the field.

@@

\fxwarning{Need to carefully introduce this section: how did we come up this this architecture? Describe archi}

Over the last years, we have been slowly ramping up explicit knowledge
representation and manipulation in the deliberative and executive layers of our
robots. Ranging from situation assessment to symbolic task planning, from
verbal interaction to event-driven execution control, we have built up a
\emph{knowledge-oriented} architecture which is now used on a daily basis on
our robots.

@@

@@

@@

\fxwarning{Introduce the paragraph}

@@

The human presence brings new requirements for robot's abilities both
at the functional and at the deliberative levels~\cite{Klein2004}. The
topics involve motion~\cite{Kulic2007,Berg2004,Madhava2006},
navigation~\cite{Althaus2004,Sisbot2007}, manipulation~\cite{Kemp2007}
in presence of humans as well as perception of human
activities~\cite{Breazeal2001,Burger2008}. Also, when
interacting with humans, robots need to incorporate communication and
collaboration abilities. Several theories dealing with
collaboration~\cite{Cohen1991,Grosz1996,Clark1996} emphasize that
collaborative tasks have specific requirements compared to individual
ones, \eg, since the robot and the person share a common goal, they
have to agree on the manner to realize it, they must show their
commitment to the goal during execution, etc. Several robotic systems
have already been built based on these
theories~\cite{Rich1997,Sidner2005,Breazeal2003} and they
all have shown benefits of this approach. They have also shown how
difficult it is to manage turn-taking between communication partners
and to interleave task realization and communication in a generic
way. Finally, today only few
systems~\cite{Fong2006,Breazeal2003,Sisbot2008} take humans into
account at all levels.

@@

\fxwarning{Rewrite conclusion}
